\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
My mistake, this text was already present under quantitative.

\begin{enumerate}
\item Visit Wikipedia’s main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today’s selected article?
\item After you have completed the tasks, fill out this survey: \textit{<survey link>} 
\end{enumerate}

Now you are done! Please stay stay at your desk until the experiment is formally over.

@@

1. Visit Wikipedia’s main page (\url{https://en.wikipedia.org/wiki/Main\_Page}). What is the topic of today’s selected article?

2. After you have completed the tasks, fill out this survey: http://bit.ly/tor-survey

>>>>

@@

\begin{enumerate}
\item Visit Wikipedia’s main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today’s selected article?
\item After you have completed the tasks, fill out this survey: \begin{NoHyper}\url{http://bit.ly/tor-survey}\end{NoHyper}
\end{enumerate}
